Refinements for open automata

### 2022-07-15 2021-Refinement/paper/refinementarticle.tex
cont.

The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$. For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly. If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata depicted in Fig.~\ref{Fig:ComposeRefine}.
\end{example}

>>>>

The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$. For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly. If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata depicted in Fig.~\ref{Fig:ComposeRefine}. As stated by the theorem, this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, the automaton resulting from the composition of the abstract \texttt{database}.
\end{example}
